### 2018-07-06 doc/plos/text/manuscript.tex
add covariance subsection

>>>>

\subsection*{Covariance}

Given that multiple surveillance sources provide data at the level of US
states, the total number of source-location pairs (``sensors'') is well into
the hundreds. Their resulting covariance is very high-dimensional, especially
relative to the amount of weekly historical training data that is typically
available (e.g. a couple of years). Further, some data sources are only
available seasonally (i.e. EPIC, ARCH), and some are relatively lacking in
training data (i.e. CDCP, EPIC). In general, partial and missing data is a
possibility for any data source.

Estimating covariance in this situation is challenging, and while the
statistical literature suggests several approaches TODO(cite a few of them),
consensus appears to be lacking.

We begin by computing the empirical pair-wise covariance of all sensors.
However, the resulting matrix does not necessarily describe multi-dimensional
covariance (i.e. it may not be positive definite). To correct this, we shrink
this matrix toward the diagonal matrix of sensor variance. The magnitude of the
shrinkage weight is chosen to maximize the multivariate normal log-likelihood
of the available data. We subsequently use the shrunken matrix as $R$ in sensor
fusion.
